\section{Natural Language Sentences}
%what did we discover during the interviews? what characteristic should the system have?
%Notice that, the description here, although rich, is at high level.
(Alejandro and Isabel)

        The company \textbf{*insert name*}, owner of the expansive supermarket chain \textbf{*insert name*}, with more than 800 locations throughout the country, finds itself in need of a new database system. The primary objective of the company is to establish a dependable system for the storage and manipulation of essential data, which is characterized by its reliability, fast performance, and its intuitive interface.

\vspace{5mm} %5mm vertical space

      The system is required to meticulously record information concerning each supermarket; shop code, location, employees, inventory, sales records, etc. Additionally, it must have information about each product, fostering uniformity across all supermarkets; product code, name, category, price, etc. The purpose for maintaining consistent product data between stores is to ensure that if a change is made in a specific item, for example base price, all the establishments will have identical information.

\vspace{5mm} %5mm vertical space

     During opening hours, data is collected and stored in each supermarket\textbf{.} This ensures that the database is always updated and its accuracy is on point. When cargo trucks arrive at the supermarket, inventory control specialists must add each batch of products to the database, so it is clear that new items have arrived. They are also intended to get in contact with the suppliers in order to keep the stock on level. Products will be identified by the product code. This and more information will be obtained from the barcode printed in the item. 

\vspace{5mm} %5mm vertical space

        Continuing the process, when an item is scanned and purchased through the cashier, the system will know exactly what product is selected from the barcode and its quantity will be decreased in the database. The receipt will also have information such as the name of the product and the price, obtained from the database. In addition to that, stock clerks will be in charge to take stock every day after the supermarket is closed, making sure the number of products in store is the same as the one in the database, or in case of disarrangement, they must update the table. They are also responsible for removing the expired items from the shelves and to remove them from the database, as well as keeping the near expiration products in front, so the customers will pick them. Overseeing these operations is the store manager, who makes sure the supermarket works smoothly. They also have a crucial role when it comes to customer services, since they are the representative of each supermarket. 
        
\vspace{5mm} %5mm vertical space

        Regarding the human resources, when a new employee is hired, the department is in charge of adding it to the database, including the information needed. Besides, promotions are also reflected in the database and when an employee is fired, it is mandatory to delete it from the system. 

\vspace{5mm} %5mm vertical space

        In the case of any system issues, IT specialists are the ones in charge. They hold an administrative role and are responsible for keeping the database well-maintained. They are also the ones that manage access privileges of each user and keep the hierarchy in order. Moreover, data analysis also plays a crucial role in the company. They can only view the data, but they are in charge of making statistics, keeping track of the employees’ performance and the best-sellers.
        
\vspace{5mm} %5mm vertical space

        One of the new additions that the company aspires to incorporate a loyalty program, where clients can subscribe in order to access a variety of benefits such as discounts and information about the products in the different establishments, as well as earning points while shopping. It will be accessible via the web page or the phone application. Consequently, the database is mandated to encompass client information.

\vspace{5mm} %5mm vertical space

        Each individual account, specifically associated with a particular user, will be uniquely identified by an email address, which will be necessary to register on the program. Clients will be required to establish a password when creating the account, which will serve as the authentication method for accessing their respective account. The system will also have to store personal information, including full name, surname, date of birth, and preferred store location. This program will be granted access to the database, from which it will retrieve the necessary data for informing the users. Cashiers are also required to scan the user card, or the QR available in the app, so clients can use their discounts and earn points when shopping.

 

