\section{Term Glossary}

%\begin{table}[!ht]
%    \centering
%    \begin{tabular}{c|c}
%         &  \\
%         & 
%    \end{tabular}

%    \caption{Caption}
%    \label{tab:my_label}
%\end{table}



%\begin{longtblr}[
%  caption = {Long Title},
%  label = {tab:test},
%]{
%  colspec = {|XX[4]|},
%  rowhead = 1,
%  hlines,
%  row{even} = {gray9},
%  row{1} = {olive9},
%} 
%
%\end{longtblr}

\begin{longtable}{|p{.20\columnwidth}|p{.30\columnwidth} |p{.20\columnwidth}|p{.20\columnwidth}|} 
\hline
\textbf{Term} & \textbf{Description} & \textbf{Synonyms} & \textbf{Connection} \\\hline

Product & An item or service that is created, manufactured, or provided for the usage of customers  & Item &  Categories, Store, Price, Quantity, ID, UPC \\\hline

Customer & An entity that purchases commodities or services from a seller or provider. & Customer & Product, Store, Receipt, Price, Manager, Employee \\\hline

Store & Physical or online location where products, goods, or items are kept, displayed, and made available for purchase by customers.& Shop &  Product, Categories, Quantity, Employee, Data Analyst   \\\hline

%Brand should be deleted? Changed to Supplier
Supplier & A company or entity that provides products and goods to the supermarket for resale to customers. & Dealer, Distributor &  Product, Store, Price, Category \\\hline

Categories &  Classifications used to organize and group similar items or entities based on shared characteristics or attributes. & Section & Product, Customer? \\\hline

Price & A certain amount of money or services that must be exchanged to acquire a particular product or service. & Cost, Fee & Product, Store, Employee?, Receipt \\\hline

Quantity in Stock &  It represents the total number of a specific product or item that is currently available for sale or use within a particular business or organization.  & Stock level & Product, Store, Employee Manager, ID, UPC \\\hline

Manager &  An individual within an organization who holds a position of authority and responsibility for overseeing and coordinating the activities of a team, department, or specific area of a company. & Head of Store & Customer, Store, Quantity, Employee \\\hline

Employee & An individual who works for an organization or employer in exchange for compensation, which may include wages, salaries, benefits, and other forms of remuneration. & Workers, Staff & Product, Customer, Store, Quantity, Manager \\\hline

Product ID & a unique and alphanumeric or numeric code or identifier assigned to a specific product to distinguish it from other items within a database.  & Product Code & Product, UPC \\\hline

UPC & stands for Universal Product Code, is a standardized and widely recognized barcode system used for product identification in the retail and manufacturing industries. It consists of a unique 12-digit numerical code that represents a specific product.  & Barcode, Product Identification & Product, ID \\\hline

Receipts &  A commercial document issued by a seller or service provider to a client, detailing the products provided, their quantity, prices and other relevant transaction information. & Product Invoice & Product, Customer, Price, ID, Store \\\hline

Data Analyst & A professional who specializes in collecting, interpreting, and transforming data into meaningful insights. & Data Manager & Product, Store \\\hline


\label{tab:termGlossary}
\end{longtable}












